Modularizing Street Map Generation \\ \vspace{8pt} \large An Adventure in Tensors

### 2013-12-12 paper/paper.tex
add more json files for images

\section{Contributions}

>>>>

\section{Conclusion}
In this paper we have presented the underlying mathematics and functional
implementation of the work described in \cite{chen}, with the goals being that a
functional implementation would easily express the mathematics and provide
modularity that the imperative implementation provide in \cite{chen} could not.
